\section{Introduction}

In this paper, we focus on the Wyner-Ziv (WZ) and Gelfand-Pinsker (GP) coding problems.
For lossy compression with a fixed distortion constraint and side information at the receiver, the WZ rate $R_{WZ}$ is the minimum achievable rate for source encoding~\cite{Wyner-it76}.
For channel coding with an input constraint and side information at the transmitter, the GP rate $R_{GP}$ is the maximum achievable information rate~\cite{Gelfand-ppi80}.
Source and channel coding problems with side information arise naturally in network information theory.
Solutions to these problems often require the use of ``binning'', where a set of codewords is partitioned into separate bins such that each bin is a good source code or channel code~\cite{Cover-2006}.

% Over the past 20 years, sparse-graph codes with iterative decoding
% have revolutionized information theory and coding. First, turbo and
% low-density parity-check (LDPC) codes demonstrated conclusively that
% codes with low-complexity decoders are not constrained by the computational
% cutoff rate~\cite{Berrou-icc93,MacKay-elet96}. Then, optimized irregular
% LDPC codes with belief-propagation (BP) decoding were proven to achieve
% capacity on the binary erasure channel (BEC) and later observed to
% approach capacity for all of the standard channel-coding problems
% (e.g., point-to-point, multiple-access, etc...)~\cite{Luby-it01,Richardson-it01*2,RU-2008}. 

% The good news does not extend automatically, however, to problems
% that require the quantization of an arbitrary sequence to a nearby
% codeword (e.g., lossy compression, WZ, and GP). 
% These problems are not easily solved via iterative decoding because the iterations only converge for a vanishing fraction of the entire sequence space.
% These problems are not easily solved via iterative decoding because the iteration only
% converges to a codeword for the sequence vectors that are not ``too
% far'' from a valid codeword. Unfortunately, this subset generally
% comprises a vanishing fraction of the entire sequence space.

% In the past few years, a number of practical constructions for these
% problems have been considered. In~\cite{Yang-asilomar03,Liveris-icip03,Sun-isit05},
% nested linear codes are designed where trellis codes are used as the
% source code and LDPC codes are used as the channel code. For the dirty-paper-coding
% problem, Erez and ten~Brink proposed nested codes combining trellis-based
% source codes with repeat-accumulate channel codes~\cite{Erez-it05}.
% In all these cases, there are non-negligible performance gaps relative
% to what is achievable for related single-user problems. In~\cite{Sun-it09},
% Sun et al.\ show that, by using a 2048-state trellis coded quantizer
% and carefully designed IRA code, a gap of about 0.63~dB from optimal
% prcoessing can be obtained for a rate of 0.25 b/s. However, the complexity
% of the trellis quantizer is somewhat prohibitive and one must optimize
% the IRA code.

%%%Replacement

Sparse-graph codes with iterative decoding have been very successful for channel coding problems.
This good news does not extend automatically, however, to problems that require the quantization of an arbitrary sequence to a nearby codeword (e.g., lossy compression, WZ, and GP).
These problems are not easily solved via iterative decoding because the iterations only converge for a vanishing fraction of the entire sequence space.
In the past few years, a number of practical constructions for these problems have been considered \cite{Yang-asilomar03,Liveris-icip03,Erez-it05,Sun-it09}.
In all these cases, there are non-negligible performance gaps relative to what is achievable for related single-user problems. 
%%%

For lossy compression, low-density generator matrix (LDGM) codes with modified versions of BP decoding can achieve practically interesting results but they appear to have a non-negligible gap to the optimal compression rate~\cite{Murayama-physreve04,Regalia-com09}.
Better results can be obtained by using guided decimation techniques where an iterative algorithm (e.g., BP or survey propagation (SP)) is used to sequentially identify bits with a large bias and then fix them to match the bias~\cite{Ciliberti-physrevlet05,Wainwright-it10}.
Building on these results, spatially-coupled (SC) LDGM codes with BP guided decimation (BPGD) were recently shown by Aref et al.~to approach the optimal compression rate for a binary symmetric source (BSS)~\cite{Aref-isit12,Aref-arxiv13}.

In this paper, we extend the approach of Aref et al. to the WZ and GP problems defined by BSSs and binary symmetric channels (BSCs).
For these problems, Wainwright and Martinian showed that compound LDGM/LDPC codes can achieve the optimal rates when maximum-likelihood processing is used~\cite{Wainwright-it09}. In this work, we show empirically that BPGD of SC compound LDGM/LDPC codes can approach the optimal WZ and GP rates.

A new complication with compound LDGM/LDPC codes is that the BPGD encoding now has the possibility of failure.
For iterative encoding with LDGM codes, encoding always succeeds but the resulting distortion depends on the code and encoder details.
For compound LDGM/LDPC codes, the compressed bits are also required to satisfy some parity checks and the iterative encoder is not guaranteed to find a valid encoding regardless of the target distortion.
This is similar to what happens when BPGD is used for constraint satisfaction problems~\cite{Montanari-arxiv07a}.
In fact, without spatial-coupling the BPGD encoder failed in every experiment.
%One benefit of compound LDGM/LDPC codes is that they can achieve the optimal rate with finite bit and check degrees.

Finally, it is important to note that the WZ and GP problems can also be solved using polar codes~\cite{Korada-it10}.
In fact, polar codes allow the deterministic construction of codes that approach the optimal rates.
The main drawback of polar codes is that their rate approaches the theoretical limit quite slowly as the block length increases.
Thus, they require very large block lengths to operate at rates close to the limit.
The precise trade-offs between SC codes and polar codes for these problems remains an interesting open problem.

%%% Local Variables: 
%%% mode: plain-tex
%%% TeX-master: "isit14"
%%% End: 
