\documentclass[conference]{IEEEtran}

\IEEEoverridecommandlockouts

\input{preamble}

\makeatletter %only needed in preamble
\renewcommand\Huge{\@setfontsize\Large{22pt}{26}}
\makeatother

\begin{document}

\title{Spatially-Coupled Codes for Side-Information Problems}

\author{Santhosh Kumar, Avinash Vem, Krishna Narayanan, Henry D. Pfister
  \thanks{This material is based upon work supported in part by the
    National Science Foundation (NSF) under Grant No. 1320924.
    Any opinions, findings, conclusions, and recommendations expressed
    in this material are those of the authors and do not necessarily
    reflect the views of these sponsors.}
   \\Department of Electrical and Computer Engineering, Texas A\&M University
}

\maketitle

\begin{abstract}
For compound LDGM/LDPC codes with maximum a posteriori (MAP) processing, Wainwright and Martinian showed that the information-theoretic rate regions of the Wyner-Ziv (WZ) and Gelfand-Pinsker (GP) problems are achievable.
For the same ensemble, these rates do not appear to be achievable with message-passing guided decimation (GD).
Fortunately, spatially-coupled (SC) codes seem to provide an elegant remedy when iterative decoding falls short of MAP decoding.
In particular, Aref et al.\ recently introduced SC LDGM codes that approach the rate-distortion region with belief-propagation guided decimation (BPGD).
In this paper, we show that SC compound LDGM/LDPC codes with BPGD can approach the rate regions of the WZ and GP problems.
\end{abstract}

\begin{IEEEkeywords}
  Belief-propagation, channel coding, convolutional LDPC codes, LDGM codes, LDPC codes, rate distortion.
\end{IEEEkeywords}

\input{intro}

\section{Background}
\input{background}

\section{Spatially-Coupled Codes and Message-Passing}
\input{coupling_mp}

\vspace{-0.0mm}
\section{Numerical Results}
\input{numerical_results}

\section{Conclusion}
We have considered SC compound LDGM/LDPC codes that achieve the rate regions of the WZ and GP side-information problems.
The decoding and encoding is based on message-passing algorithms.
The encoding is performed using BPGD algorithm.
For the WZ problem, LDGM codes were sufficient for the encoding to achieve the entire rate region.
For the GP problem, we require compound codes and the encoding here is more complicated since the LDPC bit-nodes need to satisfy additional constraints.
The structure enforced by spatial-coupling seems to be crucial for the BPGD algorithm to encode to a codeword in compound codes.
Numerical evidence is provided that shows that the SC compound codes can approach the desired rate regions.

\vspace{-0.0mm}
\bibliographystyle{ieeetr}
\bibliography{WCLabrv,WCLbib,WCLnewbib}

\end{document}
