\documentclass{beamer}

\usepackage[orientation=portrait,size=a0,scale=1.1]{beamerposter}
\usetheme{confposter}
\usepackage{exscale} % Use after theme to display integrals properly
\input{preamble}

\newlength{\columnheight}
\newlength{\onecolwid}
\newlength{\twocolwid}
\newlength{\threecolwid}
\newlength{\halfcolwid}
\newlength{\itemspace}
\newlength{\subitemspace}

\setlength{\columnheight}{105cm}
\setlength{\onecolwid}{0.3\paperwidth}
\setlength{\twocolwid}{0.3\paperwidth}
\setlength{\threecolwid}{0.3\paperwidth}
\setlength{\halfcolwid}{0.12\paperwidth}
\setlength{\itemspace}{0.35cm}
\setlength{\subitemspace}{0.1cm}

\setbeamercolor{block title}{fg=blue,bg=white}
\setbeamercolor{block body}{fg=black,bg=white}
\setbeamercolor{block alerted title}{fg=white,bg=dblue!70}
\setbeamercolor{block alerted body}{fg=black,bg=dblue!10}

\title{\LARGE Spatially-Coupled LDGM/LDPC codes for Write-Once Memories}
\author{Santhosh Kumar$^{\dagger}$, \textbf{Avinash Vem}$^{\dagger}$, Henry D. Pfister$^{\ddagger}$, Krishna Narayanan$^{\dagger}$}
\institute{Texas A\&M University$^{\dagger}$, Duke University$^{\ddagger}$}

\begin{document}
\begin{frame}
\begin{columns}[t]
  % First Column
  \begin{column}{\onecolwid}

    \vspace{0.25cm}  
    % Introduction
    \begin{block}{\Large Write-Once Memory}
      \begin{itemize}
      \item\vspace{\itemspace}  In flash memory, changing a cell from 1 to 0 is easy. 0 to 1 requires rewriting whole block
      \item\vspace{\itemspace}  Write-once memory(WOM) models such storage system
      \item\vspace{\itemspace}   Given $n$ memory units with some given state $\{0,1\}^n$, store a message $\in \{1,2,...2^{nR}\}$
      \item\vspace{\itemspace}  \textcolor{blue}{$0 \longrightarrow 1$ is allowed}. \textcolor{red}{$1 \longrightarrow 0$ is forbidden}
      \item\vspace{\itemspace}  Referred to as rate-$R$ WOM code
      \end{itemize}
    \end{block}

    % Spatially-coupled Ensemble
    \vspace{2cm}
    \begin{block}{\Large Capacity Region}
%      \resizebox{26cm}{17cm}{
%        \input{./Figures/protograph_spatially_coupled_ldpc}
%      }
      \begin{itemize}
      \item \vspace{\itemspace} In 1985, Heegard gave the capacity for $t$-write system with no read or write errors.
      \item \vspace{\itemspace} For the 2-write system it is 
            \begin{align*}
        & \Big{\{} (R_1,R_2) \mid 0 \leq R_1 <  h(\delta) , \,\,0 \leq R_2 < 1-\delta \Big{\}} 
      \end{align*}
      \item \vspace{\itemspace} WOM with read errors - Message is decoded from a noisy version of the stored vector $Y=X+\text{Ber}(p)$.
      \item \vspace{\itemspace} Capacity region is not known.
      \end{itemize}
    \end{block}

    % Main Theorems
    \vspace{2cm}
    \begin{alertblock}{\Large Main Result}
        \begin{itemize} 
        \item Objective is to construct low complexity encoding and decoding schemes that achieve the capacity region of WOM system.
        \item \vspace{\itemspace} Focus mainly on 2-write WOM system
        \begin{itemize}
			\item \vspace{\itemspace} We achieve the capacity of the 2-write noiseless WOM system.
			\item \vspace{\itemspace} For WOM system with read errors, achievable rate region is 
			    \begin{align*}
    		      R_1 &< h(\delta) - h(p), & R_2 &< 1 - \delta - h(p) .
	        \end{align*}
        \end{itemize}        
      \item \vspace{\itemspace}Extension to multi-write WOM system seems possible with BPGD.
      \end{itemize}
    \end{alertblock}

    % Preliminaries & Notation
    \vspace{2cm}
    \begin{block}{\Large Compound LDGM/LDPC Codes}
    \begin{center}
      \scalebox{2}{\input{Figures/compound_code}}
    \end{center}
        \begin{itemize}
    \item  $(n,m-k-k')$ code .
    \item Message constraints \vspace{-0.2cm}
      \begin{align*}
        u_1\oplus u_2 \oplus u_5&=s_1, &  u_1\oplus u_3 \oplus u_6&=0
      \end{align*}
    \item Codeword $(x_1,\cdots,x_9)$: \vspace{-0.2cm}
      \begin{align*}
        x_1 &= u_1 \oplus u_4, & x_2 &= u_1\oplus u_3 \cdots
      \end{align*}
    \item Parametrized by $s^k$: $\mathcal{C}(s^k)$
    \item\vspace{\itemspace} A natural coset decomposition: $\mathcal{C}=\bigcup_{s^k \in \{0,1\}^k} \mathcal{C}(s^k)$
%    \item\vspace{\itemspace} Rate of code $\mathcal{C}$ is $\frac{m-k'}{n}$
        \item\vspace{\itemspace} ``Good" source code under \textcolor{blue}{optimal encoding}
     \begin{itemize}
     \item $\exists$ a code of rate $R=1-h(\delta)+\varepsilon$ 
     \item Encodes $\mathsf{Ber}(\tfrac{1}{2})$ source with an average Hamming \textcolor{blue}{distortion at most $\delta$}
     \end{itemize}
     
       \item\vspace{\itemspace}  ``Good'' channel code under \textcolor{blue}{optimal decoding}
    \begin{itemize}
    \item $\exists$ a code of rate $R=1-h(p)-\varepsilon$
    \item When used for channel coding on $\mathsf{BSC}(p)$, message est. with \textcolor{blue}{error probability at most $\varepsilon$}
    \end{itemize}            
    \end{itemize}
  \end{block}
  \end{column}

  % Second Column
  \begin{column}{\twocolwid}
    \vspace{0.25cm}
    \begin{block}{Coding scheme for 2-write: First write}

    \begin{itemize}
    \item With message $s^k$, encode $0^n$ to $x^n$ (Distortion $\approx \delta$). Store $x^n$
    \item\vspace{\itemspace} Decoder has
      \small{
        \begin{align*}
          y_i&=x_i \oplus \mathsf{Ber}(p) \\
        \end{align*}
      }
    \vspace{-1.25cm}
    \item \vspace{\itemspace}\textcolor{blue}{Decode $x^n$} using channel code $\mathcal{C}$ and \textcolor{blue}{compute $s^k$}
          \begin{center}
		      \scalebox{1.5}{\input{Figures/coding-scheme-first-write-decode}}
		    \end{center}
    \item \vspace{\itemspace} $R_1=\tfrac{k}{n}\approx h(\delta)-h(p)$
    \end{itemize}
    \end{block}



    \vspace{2cm}
\begin{block}{Coding scheme for 2-write: Second write}
    \begin{itemize}
	    \item Need to find a \alert{consistent} codeword in $\mathcal{C}(s^k)$
    \begin{center}
      \scalebox{1.5}{\input{Figures/coding-scheme-second-write}}
    \end{center}
   		 \item Closely related to \textcolor{blue}{Binary Erasure Quantization (BEQ)} ({\footnotesize refer block below})
   		 \item \vspace{\itemspace}To map to BEQ problem , change $0$'s to $*$
	     \item \vspace{\itemspace}With message $s^k$, encode seq. to $\mathcal{C}(s^k)$
        \item \vspace{\itemspace} Decoder has
      %\small{
        \begin{align*}
          y_i&=x_i \oplus \mathsf{Ber}(p) \\
        \end{align*}
      %}
    \vspace{-2.5cm}
    \item \textcolor{blue}{Decode $x^n$} using channel code $\mathcal{C}$ and \textcolor{blue}{compute $s^k$}
    \item\vspace{\itemspace} $R_2=\tfrac{k}{n}\approx 1 - \delta - h(p)$
	\end{itemize}
\end{block}

    \vspace{2cm}
 \begin{block}{Binary Erasure Quantization}
  \begin{itemize}
  \item Quantize a sequence in $\{0,1,*\}^n$ to $x^n \in \mathcal{C} \subset \{0,1\}^n$
    \begin{itemize}
    \item \vspace{\subitemspace}$0$'s and $1$'s should \alert{match exactly}
    \item \vspace{\subitemspace}$*$'s can be changed to \textcolor{blue}{either $0$ or $1$}
    \end{itemize}
    \vspace{0.25cm}
  \item BEQ is the dual of decoding on binary erasure channel
    \begin{itemize}
    \item\vspace{\subitemspace} Martinian and Yedidia'03
    \item\vspace{\subitemspace} Can quan. all seq. with erasure pattern $e^n \in \{0,1\}^n$ to $\mathcal{C}$ \\ \hspace{3.5cm} $\Updownarrow$ \\ Chan. dec. for $\mathcal{C}^{\perp}$ can correct all vectors with eras. $1^n \oplus e^n$
    \end{itemize}
  \item\vspace{\itemspace} Choose a good (dual) code $\mathcal{C}(s^k)$
  \end{itemize}
 \end{block}


\vspace{2cm}
\begin{block}{Iterative Erasure Quantization Algorithm}
  \begin{center}
    \scalebox{1}{\input{Figures/peeling-encoder}}
  \end{center}
  \begin{itemize}
  \item \alert{Peeling type encoder}
  \begin{center}
    \begin{algorithmic}
      \WHILE{$\exists$ non-erasures in $V$}
      \IF{$\exists$ non-erased $u \in U$ such that only one of its neighbors $v \in V$ is not erased}
      \STATE Pair $(u,v)$.
      \STATE Erase $u$ and $v$.
      \ELSE
      \STATE FAIL.
      \STATE \textbf{break}.
      \ENDIF
      \ENDWHILE
    \end{algorithmic}
  \end{center}
\end{itemize}  
\end{block}
\end{column}
 
 
  % Third Column
  \begin{column}{\threecolwid}

    \vspace{0.25cm}
\begin{block}{Spatially-Coupled Compound Codes}
  \begin{center}
    \scalebox{1.5}{\input{Figures/spatially_coupled_compound_code}}
  \end{center}
 \end{block}

\vspace{2cm}
\begin{block}{Numerical Results}
\begin{itemize}
\item Noiseless WOM
\vspace{\subitemspace}
\begin{itemize}
\item $\delta^{*}=1-R$ is the threshold
\item $L=30$, Single system length $\approx 30000$
\end{itemize}
\vspace{\subitemspace}
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
LDGM/LDPC & $\delta^{*}$ & $\delta$ & $\delta$ & $\delta$ \\
$(d_v,d_c,d'_v,d'_c)$ & & $w=2$ & $w=3$ & $w=4$ \\
\hline
%$(3,3,3,6)$  & $0.500$ & $0.477$ & $0.492$ & $0.494$\\
%$(3,3,4,6)$  & $0.333$ & $0.294$ & $0.324$ & $0.326$\\
%$(3,3,5,6)$  & $0.167$ & $0.095$ & $0.156$ & $0.158$\\
$(4,4,3,6)$  & $0.500$ & $0.461$ & $0.491$ & $0.492$\\
$(4,4,4,6)$  & $0.333$ & $0.278$ & $0.323$ & $0.325$\\
$(4,4,5,6)$  & $0.167$ & $0.086$ & $0.155$ & $0.159$\\
$(5,5,3,6)$  & $0.500$ & $0.436$ & $0.488$ & $0.491$\\
$(5,5,4,6)$  & $0.333$ & $0.260$ & $0.320$ & $0.324$\\
$(5,5,5,6)$  & $0.167$ & $0.079$ & $0.154$ & $0.159$\\
\hline  
\end{tabular}
\end{center}
\item \vspace{\itemspace}WOM with Read Errors
\vspace{\subitemspace}
\begin{itemize}
\item $\delta^{*}$ and $p^{*}$ are the achievable thresholds
\item $L=30$, Single system length $\approx 30000$
\end{itemize}
\vspace{\subitemspace}
  \begin{center}
    \begin{tabular}{|c|c|c|c|}
      \hline
      LDGM/LDPC & $w$ & $(\delta^{*},p^*)$ & $(\delta,p)$ \\
      $(d_v,d_c,d'_v,d'_c)$ &  &  & \\
      \hline
      $(3,3,4,6)$ & $3$ & $(0.333,0.0615)$ & $(0.321,0.0585)$ \\
      $(3,3,4,8)$ & $3$ & $(0.500,0.0417)$ & $(0.490,0.0387)$ \\
      $(3,3,6,8)$ & $4$ & $(0.250,0.0724)$ & $(0.239,0.0684)$ \\
      $(4,4,4,6)$ & $4$ & $(0.333,0.0615)$ & $(0.324,0.0585)$ \\
      $(4,4,4,8)$ & $4$ & $(0.500,0.0417)$ & $(0.492,0.0387)$ \\
      $(4,4,6,8)$ & $4$ & $(0.250,0.0724)$ & $(0.241,0.0694)$ \\
      \hline  
    \end{tabular}
  \end{center}

\end{itemize}
\end{block}

    \setbeamercolor{block alerted title}{fg=black,bg=norange} % Change the alert block title colors
    \setbeamercolor{block alerted body}{fg=black,bg=white} % Change the alert block body colors

    \vspace{2.5cm}
\begin{alertblock}{Conclusion}
        \begin{itemize}
    \item Spatially-coupled compound codes achieve the capacity of 2-write systems \vspace{0.2cm}
    \item \vspace{\itemspace}\textcolor{red}{Coupling structure} is crucial 
      \begin{itemize}
      \item to achieve optimum thresholds under practical schemes 
      \item also for the encoding to succeed 
      \end{itemize}
    \item \vspace{\itemspace} Will BPGD work for \textcolor{blue}{multi-write systems}?
    \end{itemize}
\end{alertblock}

    % Bibliography
    \vspace{2.5cm}
    \begin{block}{References}

      \begin{thebibliography}{10}
	\bibitem{Heegard}
Heegard, Chris. "On the capacity of permanent memory." \emph{ IEEE Trans. \ Inform \ Theory}, vol.~31, no.~1,pp. ~34-42,1985.

\bibitem{Bruck}
E.~E.~Gad, Eyal En, Y.~Li, J.~Bruck, "Rewriting flash memories by message passing."in
\emph{IEEE Int. Symp. Inf. Theory}, June 2015.

		\bibitem{Wainwright-Martinian}
		Wainwright, Martin J., Elitza Maneva, and E.~Martinian. "Lossy source compression using low-density generator matrix 		codes: Analysis and algorithms." \emph{IEEE Trans. \ Inform \ Theory}, vol.~56, no.~3, pp. 1351-1368, 2010. 
		\vspace{1cm}

\bibitem{Hsu-Anasta}
Hsu, Chun-Hao, and A.~Anastasopoulos. "Capacity-achieving codes with bounded graphical complexity and maximum likelihood decoding." \emph{IEEE Trans. \ Inform \ Theory} on vol.~56, no.~3, pp.~992-1006, 2010.

      \bibitem{Martinian03}
        E.~Martinian and J.~S. Yedidia, "Iterative quantization using codes on graphs." in 
        \emph{ Proc. Allerton. Conf. Comm., and Comp., } 2003.
        \vspace{1cm}

 		\end{thebibliography}
	  \end{block}
 
  \end{column}
\end{columns}
\end{frame}
\end{document}
