%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  New template code for TAMU Theses and Dissertations starting Fall 2016.  
%
%
%  Author: Sean Zachary Roberson
%  Version 3.17.06
%  Last Updated: 6/15/2017
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                           ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{ACKNOWLEDGMENTS}
\addcontentsline{toc}{chapter}{ACKNOWLEDGMENTS}  % Needs to be set to part, so the TOC doesnt add 'CHAPTER ' prefix in the TOC.

It was a long, rewarding and fulfilling journey to my Ph. D. degree. This would not have been possible if not for the support and encouragement of a lot of people starting from my teachers and friends in high school to my professors, friends and colleagues at Texas A\&M university. My heartfelt gratitude and thanks go out to each and everyone who helped me and stood by me.

\indent First and foremost, I would like to thank my advisor Dr. Krishna Narayanan for his guidance throughout the past six years of my graduate studies. He was always available, literally a knock-on-the-door away, with plenty of time for me. I will be forever indebted to his teachings, support and the valuable directions he provided in times of struggle. He taught me coding and information theory courses in my first two semesters at Texas A\& M University and his passionate teaching arose the curiosity in me and laid the foundations for my subsequent forays into these rich and beautiful areas of research. I am truly fortunate to have spent the formative years of my academic and professional career under the tutelage of such a wonderful academic and a warm person. I hope to carry his legacy forward.

I would like to thank Professors Jean-Francois Chamberland, Arun Srinivasa, and Alex Sprintson for their time in serving on my thesis committee. I am thankful for their insights.

I am thankful to a lot of friends and colleagues whose company and camaraderie made this journey all the more enjoyable. I want to reminisce and thank my roommates Nilu, Rhushabh `Sir' for all the late night discussions, Shweta, Suraj, Sneha, Gupta \textit{et al}., from my second-family `Nagle' group for the innumerable weekends spent in laughter and banter, Manjusha, Kartheek and Siddhitha for their affection. I am also thankful to my lab-mates Arvind Yedla, for the crazy parties and fun times spent in and `around' Eugenes, Santhosh Vanaparthy, for the hours long discussions we had on a wide range of topics varying from madness of mathematicians like Paul Dirac to the importance/stupidity of sports etc., Rahul, Emmadi, Jerry Huang, Engin, Yung-Yih Jian, Fatemeh, Nagaraj, Paul, Arman, and several others.

Above all, I am forever grateful to Dakshna for all the wonderful times we spent in College Station, for being with me in the ups and downs of this journey, for providing the care, comfort, motivation, encouragement, guidance and support when I needed them. At a moment of looking back, I want to remember my uncle Narasimha Reddy for his assistance and encouragement in my pursuing higher studies. Although no longer with us, he continues to inspire me by the hard work and love he showed for his family.

Finally, I express my deepest gratitude to my parents, Ranga Reddy and Andalamma, and my little sister Anu for their unconditional love and support and for the immense faith they have always shown in me. I cannot thank enough, my mother for all the sacrifices she made to ensure our happiness, and my father for engaging me in all my inane questions in my childhood, his insistence that I learn the mathematics and the sciences in the \textit{right} way and for prioritizing the higher education of me and my sister above all else. I will be forever indebted to them.
\pagebreak{}